---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "90%"
)
```

# translated

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/translated)](https://CRAN.R-project.org/package=translated)
<!-- badges: end -->

{translated} is a complex internationalization system made easy. Provide a directory where localization JSON files are stored and access entries from any place in your code. Various features are incorporated: recursive string interpolation, custom plural form rules, entry grouping, inheriting localization data from other dialects (see [differences between British and American English](https://en.wikipedia.org/wiki/Comparison_of_American_and_British_English) for a canonical example), and more.

## Installation

You can install the development version of {translated} from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ttscience/translated")
```

## How to use

To start using {translated} in your project, specify where to find localization JSON files:

```{r set_path}
library(translated)
# Below is the path to examples shipped with this package
path <- system.file("examples", package = "translated")
trans_path(path)
```

### Basic usage

Processing localization data is done behind the curtains. The user can focus on using the entries:

```{r trans_title_en}
trans("title")
```

This was the localization for the default locale, i.e. `en_US` (United States English). The currently set locale can be checked with:

```{r check_locale}
trans_locale()
```

To set a different locale (e.g. `pl_PL` or `pl` for short, my native language), simply pass it as an argument to the same function. Both mentioned forms are acceptable (plus the form with encoding included, for example `pl_PL.UTF-8`), so we'll use the simpler one:

```{r set_locale}
trans_locale("pl")
```

The localization immediately changes:

```{r trans_title_pl}
trans("title")
```

### String interpolation

Some entries can have gaps to fill with variable values. They are denoted with braces `{}` inside translation text, e.g. `"Courtney is {age} years old."`. Pass these variables as named parameters to `trans()` function (and don't worry, unused parameters are ignored). Most often they'll be strings, but anything coercible to string is valid, especially numbers:

```{r trans_button_pl}
trans("btn_insert", number = 4)
```

### Plural forms

It is up to the user to provide singular and plural forms for each entry where it's necessary. {translated} provides the user with an easy method to make it work: all forms for an entry are stored in a list. With an appropriate number-to-form converter, the user only has to supply the number as `.n` parameter:

```{r trans_with_n}
trans("nouns.cat", .n = 5)
trans("nouns.cat", .n = 1)
```

### Other features

To see more details about what is possible, see the vignettes.

## Dependency graph

{translated} is meant to be lightweight, so only the key packages are imported:

```{r deepdep, echo=FALSE}
deepdep::plot_dependencies("translated", depth = 4, local = TRUE)
```
